Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-25 paper/paper.tex
backend -> back end

Probabilistic programming systems \cite{GMR+08,MSP14,WVM14,GS15}
represent generative models as programs written in a specialized
language that provides syntax for the definition and conditioning of
random variables. The code for such models is generally concise,
modular, and easy to modify or extend. Typically inference can be
performed for any probabilistic program using one or more generic
inference techniques provided by the system backend, such as
Metropolis-Hastings \cite{WSG11,MSP14,YHG14}, Hamiltonian Monte Carlo
\cite{SDT14}, expectation propagation \cite{MWG+10}, and extensions
of Sequential Monte Carlo \cite{WVM14,MYM+15,PWD+14} methods.
These generic techniques may be less statistically efficient
than techniques tailored to a specific model. However,
probabilistic programming facilitates simpler implementations of
models making the inference inherently faster.
\jw{I'm not sure I understand how PP facilitates simpler implmenetations that make inference inherently faster.}

>>>>

Probabilistic programming systems \cite{GMR+08,MSP14,WVM14,GS15}
represent generative models as programs written in a specialized
language that provides syntax for the definition and conditioning of
random variables. The code for such models is generally concise,
modular, and easy to modify or extend. Typically inference can be
performed for any probabilistic program using one or more generic
inference techniques provided by the system back end, such as
Metropolis-Hastings \cite{WSG11,MSP14,YHG14}, Hamiltonian Monte Carlo
\cite{SDT14}, expectation propagation \cite{MWG+10}, and extensions
of Sequential Monte Carlo \cite{WVM14,MYM+15,PWD+14} methods.
These generic techniques may be less statistically efficient
than techniques tailored to a specific model. However,
probabilistic programming facilitates simpler implementations of
models making the inference inherently faster.
\jw{I'm not sure I understand how PP facilitates simpler implementations that make inference inherently faster.}
